Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-24 paper.qmd
Added proj for twisted patterns

>>>>

<!--proj for twisted pattern-->
```{r}
#| label: mnist-model-proj-twisted
## fourth projection
projection <- cbind(
  c(-0.03265,-0.43663,0.02143,0.07384,0.26237,0.20909,0.32398,-0.34487,0.03723,-0.04418),
  c(0.52862,-0.14177,0.20045,-0.37753,-0.09552,0.08851,0.07168,0.09255,-0.15653,-0.00030))

mnist_proj_tsne_model4 <- ggplot() +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c",
    linewidth = 0.5) +
  # geom_point(
  #   #size = 0.2,
  #   alpha = 0.2) +
  # scale_color_manual(values = c("#000000", "#e41a1c")) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 2) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-1, 1)) +
  ylim(c(-1, 1)) +
  interior_annotation("d") +
  theme(
    legend.position = "none"
  )

## fifth projection
projection <- cbind(
  c(-0.36688,-0.10781,-0.15474,-0.23005,-0.20194,-0.10841,-0.32443,0.04531,-0.36514,-0.14546),
  c(0.34256,-0.16215,-0.18747,-0.08515,-0.28689,-0.32807,0.28372,0.20894,-0.16990,0.09181))

projection_scaled <- projection * 2.3

mnist_proj_tsne_model5 <- ggplot() +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#33a02c",
    linewidth = 0.5) +
  # geom_point(
  #   #size = 0.2,
  #   alpha = 0.2) +
  # scale_color_manual(values = c("#000000", "#e41a1c")) +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 2) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-1, 1)) +
  ylim(c(-1, 1)) +
  interior_annotation("d") +
  theme(
    legend.position = "none"
  )

```{r}
#| label: fig-mnist-tri-proj-twisted
#| fig-pos: H
#| fig-height: 10
#| fig-width: 10
#| fig-cap: "twisted pattern"

free(trimesh_removed_mnist) + free(trimesh_removed_mnist) + mnist_proj_tsne_model4 + mnist_proj_tsne_model5 +
  plot_layout(ncol = 2)
```
